An investigation into the contentious phylogenetic results of the *Mixta* species

### 2021-04-18 Manuscript/Manuscript_Paper.Rmd
Update Manuscript_Paper.Rmd

# Results
Twelve and twenty-three unique models were used for nucleotide (Table 2) and amino acid sequences (Table 3) were needed to create phylogenetic gene trees.

>>>>

# Results
```{r Table2, echo=FALSE, message=FALSE, warning=FALSE, fig.cap=TRUE}
PM_NT <- read.csv("C:/Users/Kim/OneDrive/2020_3Fall/Biology_396/O10_Tables_and_Figures/Table2_PmodelsNT.csv", stringsAsFactors = FALSE)

kable(PM_NT, caption = "Table 2. According to model testing and the lowest BIC for nucleotide sequences, the number of genes required each phylogenetic tree model.")

```

# Old Results
Twelve and twenty-three unique models were used for nucleotide (Table 2) and amino acid sequences (Table 3) were needed to create phylogenetic gene trees.
